---
title: "Business Intelligence Lab Submission Markdown"
author: "Lumin"
date: "1/10/23"
output:
  github_document:
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
always_allow_html: true
editor_options:
  chunk_output_type: console
---


# Student Details

+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one student name, group, and ID per line; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                      |
|                                                   | 1.  112827 - A - Mungai Kenneth                                                                                |
|                                                   |                                                                                                      |
|                                                   | 2.  134265 - A - Emmanuel Kiptoo                                                                            |
|                                                   |                                                                                                      |
|                                                   | 3.  123324 - B - Kelly Noella Sota                                                                                |
|                                                   |                                                                                                      |
|                                                   | 4.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 5.  ID - Group - Name                                                                                |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   |    Lumin                                                                                                  |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                              |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                             |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                          |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                           |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

**Note:** the following "*R Markdown*" options have been set as the defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Step 1: Install and Load Required Packages:
In this step, we ensure that the necessary R packages are installed and loaded. Packages are collections of R functions, data, and compiled code that extend the functionality of R. The install.packages() function is used to install packages, and library() is used to load them.

```{r Your First Code Chunk}
# Consider a library as the location where packages are stored.
# Execute the following command to list all the libraries available in your
# computer:
.libPaths()

# One of the libraries should be a folder inside the project if you are using
# renv

# Then execute the following command to see which packages are available in
# each library:
lapply(.libPaths(), list.files)


# If renv::restore() did not install the "languageserver" package (required to
# use R for VS Code), then it can be installed manually as follows (restart R
# after executing the command):
if (!is.element("languageserver", installed.packages()[, 1])) {
  install.packages("languageserver", dependencies = TRUE)
}
require("languageserver")

## dplyr - For data manipulation ----
if (!is.element("dplyr", installed.packages()[, 1])) {
  install.packages("dplyr", dependencies = TRUE)
}
require("dplyr")

## ggplot2 - For data visualizations using the Grammar for Graphics package ----
if (!is.element("ggplot2", installed.packages()[, 1])) {
  install.packages("ggplot2", dependencies = TRUE)
}
require("ggplot2")

## ggrepel - Additional options for the Grammar for Graphics package ----
if (!is.element("ggrepel", installed.packages()[, 1])) {
  install.packages("ggrepel", dependencies = TRUE)
}
require("ggrepel")

## ggraph - Additional options for the Grammar for Graphics package ----
if (!is.element("ggraph", installed.packages()[, 1])) {
  install.packages("ggraph", dependencies = TRUE)
}
require("ggraph")

## tidytext - For text mining ----
if (!is.element("tidytext", installed.packages()[, 1])) {
  install.packages("tidytext", dependencies = TRUE)
}
require("tidytext")

## tidyr - To tidy messy data ----
if (!is.element("tidyr", installed.packages()[, 1])) {
  install.packages("tidyr", dependencies = TRUE)
}
require("tidyr")

## widyr - To widen, process, and re-tidy a dataset ----
if (!is.element("widyr", installed.packages()[, 1])) {
  install.packages("widyr", dependencies = TRUE)
}
require("widyr")

## gridExtra - to arrange multiple grid-based plots on a page ----
if (!is.element("gridExtra", installed.packages()[, 1])) {
  install.packages("gridExtra", dependencies = TRUE)
}
require("gridExtra")

## knitr - for dynamic report generation ----
if (!is.element("knitr", installed.packages()[, 1])) {
  install.packages("knitr", dependencies = TRUE)
}
require("knitr")

## kableExtra - for nicely formatted output tables ----
if (!is.element("kableExtra", installed.packages()[, 1])) {
  install.packages("kableExtra", dependencies = TRUE)
}
require("kableExtra")

## formattable -  To create a formattable object ----
# A formattable object is an object to which a formatting function and related
# attributes are attached.
if (!is.element("formattable", installed.packages()[, 1])) {
  install.packages("formattable", dependencies = TRUE)
}
require("formattable")

## circlize - To create a cord diagram or visualization ----
# by Gu et al. (2014)
if (!is.element("circlize", installed.packages()[, 1])) {
  install.packages("circlize", dependencies = TRUE)
}
require("circlize")

## memery - For creating data analysis related memes ----
# The memery package generates internet memes that optionally include a
# superimposed inset plot and other atypical features, combining the visual
# impact of an attention-grabbing meme with graphic results of data analysis.
if (!is.element("memery", installed.packages()[, 1])) {
  install.packages("memery", dependencies = TRUE)
}
require("memery")

## magick - For image processing in R ----
if (!is.element("magick", installed.packages()[, 1])) {
  install.packages("magick", dependencies = TRUE)
}
require("magick")

## yarrr - To create a pirate plot ----
if (!is.element("yarrr", installed.packages()[, 1])) {
  install.packages("yarrr", dependencies = TRUE)
}
require("yarrr")

## radarchart - To create interactive radar charts using ChartJS ----
if (!is.element("radarchart", installed.packages()[, 1])) {
  install.packages("radarchart", dependencies = TRUE)
}
require("radarchart")

## igraph - To create ngram network diagrams ----
if (!is.element("igraph", installed.packages()[, 1])) {
  install.packages("igraph", dependencies = TRUE)
}
require("igraph")

## wordcloud2 - For creating wordcloud by using 'wordcloud2.JS ----
if (!is.element("wordcloud2", installed.packages()[, 1])) {
  install.packages("wordcloud2", dependencies = TRUE)
}
require("wordcloud2")

## readr - Load datasets from CSV files ----
if (!is.element("readr", installed.packages()[, 1])) {
  install.packages("readr", dependencies = TRUE)
}
require("readr")
library(readr)
```


# Step 2: Customize the Visualizations, Tables, and Colour Scheme:
In this step, we're customizing the appearance of the visualizations, tables, and color scheme to enhance the output.
theme_set(theme_minimal()): This sets the theme for the plots to a minimalistic style. It affects the overall look of the plots.
options(scipen = 999): This disables scientific notation when printing numbers. It ensures that large numbers are displayed in a readable format.

```{r Your Second Code Chunk}
# STEP 2. Customize the Visualizations, Tables, and Colour Scheme ----
# The following defines a blue-grey colour scheme for the visualizations:
## shades of blue and shades of grey
blue_grey_colours_11 <- c("#27408E", "#304FAF", "#536CB5", "#6981c7", "#8da0db",
                          "#dde5ec", "#c8c9ca", "#B9BCC2", "#A7AAAF", "#888A8E",
                          "#636569")

blue_grey_colours_6 <- c("#27408E", "#304FAF", "#536CB5",
                         "#B9BCC2", "#A7AAAF", "#888A8E")

blue_grey_colours_4 <- c("#27408E", "#536CB5",
                         "#B9BCC2", "#888A8E")

blue_grey_colours_2 <- c("#27408E",
                         "#888A8E")

blue_grey_colours_1 <- c("#6981c7")

# Custom theme for visualizations
blue_grey_theme <- function() {
  theme(
    axis.ticks = element_line(
                              linewidth = 1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    axis.text = element_text(
                             face = "bold", color = "#3f3f41",
                             size = 12, hjust = 0.5),
    axis.title = element_text(face = "bold", color = "#3f3f41",
                              size = 14, hjust = 0.5),
    plot.title = element_text(face = "bold", color = "#3f3f41",
                              size = 16, hjust = 0.5),
    panel.grid = element_line(
                              linewidth = 0.1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    panel.background = element_rect(fill = "#f3eeee"),
    legend.title = element_text(face = "plain", color = "#3f3f41",
                                size = 12, hjust = 0),
    legend.position = "right"
  )
}

# Customize the text tables for consistency using HTML formatting
kable_theme <- function(dat, caption) {
  kable(dat, "html", escape = FALSE, caption = caption) %>%
    kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                  full_width = FALSE)
}

library(readr)
```


# Step 3: Load the Dataset:

```{r Your Third Code Chunk}
student_performance_dataset <-
  read_csv("/home/ki3ani/BBT4206-R-Lab2b-of15-EDAForQualitativeData-lumin/markdown/performance-dataset.csv",
           col_types =
             cols(
               class_group = col_factor(levels = c("A", "B", "C")),
               gender = col_factor(levels = c("1", "0")),
               YOB = col_date(format = "%Y"),
               regret_choosing_bi = col_factor(levels = c("1", "0")),
               drop_bi_now = col_factor(levels = c("1", "0")),
               motivator = col_factor(levels = c("1", "0")),
               read_content_before_lecture =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               anticipate_test_questions =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               answer_rhetorical_questions =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               find_terms_I_do_not_know =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               copy_new_terms_in_reading_notebook =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               take_quizzes_and_use_results =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               reorganise_course_outline =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               write_down_important_points =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               space_out_revision =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               studying_in_study_group =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               schedule_appointments =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               goal_oriented = col_factor(levels = c("1", "0")),
               spaced_repetition =
                 col_factor(levels = c("1", "2", "3", "4")),
               testing_and_active_recall =
                 col_factor(levels = c("1", "2", "3", "4")),
               interleaving = col_factor(levels = c("1", "2", "3", "4")),
               categorizing = col_factor(levels = c("1", "2", "3", "4")),
               retrospective_timetable =
                 col_factor(levels = c("1", "2", "3", "4")),
               cornell_notes = col_factor(levels = c("1", "2", "3", "4")),
               sq3r = col_factor(levels = c("1", "2", "3", "4")),
               commute = col_factor(levels = c("1", "2", "3", "4")),
               study_time = col_factor(levels = c("1", "2", "3", "4")),
               repeats_since_Y1 = col_integer(),
               paid_tuition = col_factor(levels = c("0", "1")),
               free_tuition = col_factor(levels = c("0", "1")),
               extra_curricular = col_factor(levels = c("0", "1")),
               sports_extra_curricular = col_factor(levels = c("0", "1")),
               exercise_per_week = col_factor(levels = c("0", "1", "2", "3")),
               meditate = col_factor(levels = c("0", "1", "2", "3")),
               pray = col_factor(levels = c("0", "1", "2", "3")),
               internet = col_factor(levels = c("0", "1")),
               laptop = col_factor(levels = c("0", "1")),
               family_relationships =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               friendships = col_factor(levels = c("1", "2", "3", "4", "5")),
               romantic_relationships =
                 col_factor(levels = c("0", "1", "2", "3", "4")),
               spiritual_wellnes =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               financial_wellness =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               health = col_factor(levels = c("1", "2", "3", "4", "5")),
               day_out = col_factor(levels = c("0", "1", "2", "3")),
               night_out = col_factor(levels = c("0", "1", "2", "3")),
               alcohol_or_narcotics =
                 col_factor(levels = c("0", "1", "2", "3")),
               mentor = col_factor(levels = c("0", "1")),
               mentor_meetings = col_factor(levels = c("0", "1", "2", "3")),
               `Attendance Waiver Granted: 1 = Yes, 0 = No` =
                 col_factor(levels = c("0", "1")),
               GRADE = col_factor(levels = c("A", "B", "C", "D", "E"))),
           locale = locale())

View(student_performance_dataset)

# Dimensions
dim(student_performance_dataset)

# Data Types
sapply(student_performance_dataset, class)
glimpse(student_performance_dataset)

# Summary of each variable
summary(student_performance_dataset)
library(readr)
```

# Step 4: Create a Subset of the Data:
Sometimes, we don't need all the data—just a part of it. This step is like picking only the candies you like from a big box.
```{r Your Fourth Code Chunk}
evaluation_per_group_per_gender <- student_performance_dataset %>% # nolint
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  select(class_group, gender,
         `Student's Gender`, `Average Course Evaluation Rating`) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  group_by(class_group, `Student's Gender`) %>%
  summarise(average_evaluation_rating =
              mean(`Average Course Evaluation Rating`)) %>%
  arrange(desc(average_evaluation_rating), .by_group = TRUE)

# Plain tabular output
View(evaluation_per_group_per_gender)

# Decorated tabular output
evaluation_per_group_per_gender %>%
  rename(`Class Group` = class_group) %>%
  rename(`Average Course Evaluation Rating` = average_evaluation_rating) %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`) %>%
  mutate(`Average Course Evaluation Rating` =
           color_tile("#B9BCC2", "#536CB5")
           (`Average Course Evaluation Rating`)) %>%
  kable("html", escape = FALSE, align = "c",
        caption = "Course Evaluation Rating per Group and per Gender") %>%
  kable_styling(bootstrap_options =
                  c("striped", "condensed", "bordered"),
                full_width = FALSE)

# Decorated visual bar chart
evaluation_per_group_per_gender %>%
  ggplot() +
  geom_bar(aes(x = class_group, y = average_evaluation_rating,
               fill = `Student's Gender`),
           stat = "identity", position = "dodge") +
  expand_limits(y = 0) +
  blue_grey_theme() +
  scale_fill_manual(values = blue_grey_colours_2) +
  ggtitle("Course Evaluation Rating per Group and per Gender") +
  labs(x = "Class Group", y = "Average Rating")

library(readr)
```

# Step 5: Data Cleansing for Qualitative Data:
This step involves cleaning up text data, which might involve removing unnecessary spaces, converting text to lowercase, or handling missing values.

```{r Your Fifth Code Chunk}
## Contractions ----

# Contractions in the English language are shortened forms of words or phrases
# created by combining two words and replacing one or more letters with an
# apostrophe ('), often for the purpose of making speech or writing more
# concise and informal. Contractions are often used in informal speech and
# writing but are generally avoided in formal writing, such as academic papers
# or business reports.

# A function to expand contractions in an English-language source (assuming
# that the students did not respond in sheng or Kiswahili).
expand_contractions <- function(doc) {
  doc <- gsub("I'm", "I am", doc, ignore.case = TRUE)
  doc <- gsub("you're", "you are", doc, ignore.case = TRUE)
  doc <- gsub("he's", "he is", doc, ignore.case = TRUE)
  doc <- gsub("she's", "she is", doc, ignore.case = TRUE)
  doc <- gsub("it's", "it is", doc, ignore.case = TRUE)
  doc <- gsub("we're", "we are", doc, ignore.case = TRUE)
  doc <- gsub("they're", "they are", doc, ignore.case = TRUE)
  doc <- gsub("I'll", "I will", doc, ignore.case = TRUE)
  doc <- gsub("you'll", "you will", doc, ignore.case = TRUE)
  doc <- gsub("he'll", "he will", doc, ignore.case = TRUE)
  doc <- gsub("she'll", "she will", doc, ignore.case = TRUE)
  doc <- gsub("it'll", "it will", doc, ignore.case = TRUE)
  doc <- gsub("we'll", "we will", doc, ignore.case = TRUE)
  doc <- gsub("they'll", "they will", doc, ignore.case = TRUE)
  doc <- gsub("won't", "will not", doc, ignore.case = TRUE)
  doc <- gsub("can't", "cannot", doc, ignore.case = TRUE)
  doc <- gsub("n't", " not", doc, ignore.case = TRUE)
  return(doc)
}

# Evaluation likes and wishes
evaluation_likes_and_wishes <- student_performance_dataset %>%
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  rename(`Class Group` = class_group) %>%
  rename(Likes = `D - 1. \nWrite two things you like about the teaching and learning in this unit so far.`) %>% # nolint
  rename(Wishes = `D - 2. Write at least one recommendation to improve the teaching and learning in this unit (for the remaining weeks in the semester)`) %>% # nolint
  select(`Class Group`,
         `Student's Gender`, `Average Course Evaluation Rating`,
         Likes, Wishes) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  arrange(`Class Group`)

# Before expanding contractions (See row number 4)
View(evaluation_likes_and_wishes)

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, expand_contractions) # nolint
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, expand_contractions) # nolint

# After expanding contractions
View(evaluation_likes_and_wishes)

## Special Characters and Lower Case ----
# NOTE: The special characters should be removed *after* expanding the
# contractions

# A function to remove special characters
# Remember the use of regular expressions in the
# BBT3104: Advanced Database Systems course

# A tutorial on regular expressions: https://regexone.com/
# To test your regular expression: https://regexr.com/

remove_special_characters <- function(doc) {
  gsub("[^a-zA-Z0-9 ]", "", doc, ignore.case = TRUE)
}

# Before removing special characters (See row number 11)
View(evaluation_likes_and_wishes)

evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, remove_special_characters) # nolint
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, remove_special_characters) # nolint

# Convert everything to lower case (to standardize the text)
evaluation_likes_and_wishes$Likes <- sapply(evaluation_likes_and_wishes$Likes, tolower) # nolint
evaluation_likes_and_wishes$Wishes <- sapply(evaluation_likes_and_wishes$Wishes, tolower) # nolint

# After removing special characters and converting everything to lower case
View(evaluation_likes_and_wishes)

# [OPTIONAL] You can save the file as a CSV at this point
write.csv(evaluation_likes_and_wishes,
          file = "/home/ki3ani/BBT4206-R-Lab2b-of15-EDAForQualitativeData-lumin/markdown/evaluation_likes_and_wishes.csv",
          row.names = FALSE)

# Additional examples can be seen here:
head(sample(stop_words$word, 20), 20)

# You can also create a list of words that you would like to censor
undesirable_words <- c("wow", "lol", "none", "na")

evaluation_likes_filtered <- evaluation_likes_and_wishes %>% # nolint
  # We start by tokenization (unnesting words). This is from the variable
  # "Like" into the variable "word".
  unnest_tokens(word, Likes) %>%
  # Then we remove stopwords using an anti-join (remember this from the
  # BBT3104: Advanced Database Systems course)
  # Anti-join: do not join where the word is in the list of stopwords
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  # Censor or filter out unwanted words
  filter(!word %in% undesirable_words) %>%
  # Include only words that are more than 3 characters long (assuming that
  # these are the words that are meaningful)
  filter(nchar(word) > 3) %>%
  # We then rename the variable "word" for ease of use.
  rename(`Likes (tokenized)` = word) %>%
  # We focus only on the likes in this data frame
  select(-Wishes)

# Lastly, we save the created data frame as a CSV file:
write.csv(evaluation_likes_filtered,
          file = "/home/ki3ani/BBT4206-R-Lab2b-of15-EDAForQualitativeData-lumin/markdown/evaluation_likes_filtered.csv",
          row.names = FALSE)

# The same is done to create a data frame for the "wishes" only
evaluation_wishes_filtered <- evaluation_likes_and_wishes %>% # nolint
  unnest_tokens(word, Wishes) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes (tokenized)` = word) %>%
  select(-Likes)

write.csv(evaluation_wishes_filtered,
          file = "/home/ki3ani/BBT4206-R-Lab2b-of15-EDAForQualitativeData-lumin/markdown/evaluation_wishes_filtered.csv",
          row.names = FALSE)

library(readr)
```

