---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your group name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
always_allow_html: true
---

# Student Details

+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one student name, group, and ID per line; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                      |
|                                                   | 1.  123324 - B - Kelly Noella Sota                                                                   |
|                                                   |                                                                                                      |
|                                                   | 2.  Kenneth Kimathi                                                                                  |
|                                                   |                                                                                                      |
|                                                   | 3.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 4.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 5.  ID - Group - Name                                                                                |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   |                                                                                                      |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                              |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                             |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                          |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                           |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

**Note:** the following "*R Markdown*" options have been set as the defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

These snippets are designed to generate visualizations for course evaluation data, specifically focusing on evaluation likes, wishes, and other related aspects(gender, class group).

```{r First Code Chunck}
## dplyr - For data manipulation ----
if (!is.element("dplyr", installed.packages()[, 1])) {
  install.packages("dplyr", dependencies = TRUE)
}
require("dplyr")

## ggplot2 - For data visualizations using the Grammar for Graphics package ----
if (!is.element("ggplot2", installed.packages()[, 1])) {
  install.packages("ggplot2", dependencies = TRUE)
}
require("ggplot2")

## ggrepel - Additional options for the Grammar for Graphics package ----
if (!is.element("ggrepel", installed.packages()[, 1])) {
  install.packages("ggrepel", dependencies = TRUE)
}
require("ggrepel")

## ggraph - Additional options for the Grammar for Graphics package ----
if (!is.element("ggraph", installed.packages()[, 1])) {
  install.packages("ggraph", dependencies = TRUE)
}
require("ggraph")

## tidytext - For text mining ----
if (!is.element("tidytext", installed.packages()[, 1])) {
  install.packages("tidytext", dependencies = TRUE)
}
require("tidytext")

## tidyr - To tidy messy data ----
if (!is.element("tidyr", installed.packages()[, 1])) {
  install.packages("tidyr", dependencies = TRUE)
}
require("tidyr")

## widyr - To widen, process, and re-tidy a dataset ----
if (!is.element("widyr", installed.packages()[, 1])) {
  install.packages("widyr", dependencies = TRUE)
}
require("widyr")

## gridExtra - to arrange multiple grid-based plots on a page ----
if (!is.element("gridExtra", installed.packages()[, 1])) {
  install.packages("gridExtra", dependencies = TRUE)
}
require("gridExtra")

## knitr - for dynamic report generation ----
if (!is.element("knitr", installed.packages()[, 1])) {
  install.packages("knitr", dependencies = TRUE)
}
require("knitr")

## kableExtra - for nicely formatted output tables ----
if (!is.element("kableExtra", installed.packages()[, 1])) {
  install.packages("kableExtra", dependencies = TRUE)
}
require("kableExtra")

## formattable -  To create a formattable object ----
# A formattable object is an object to which a formatting function and related
# attributes are attached.
if (!is.element("formattable", installed.packages()[, 1])) {
  install.packages("formattable", dependencies = TRUE)
}
require("formattable")

## circlize - To create a cord diagram or visualization ----
# by Gu et al. (2014)
if (!is.element("circlize", installed.packages()[, 1])) {
  install.packages("circlize", dependencies = TRUE)
}
require("circlize")

## memery - For creating data analysis related memes ----
# The memery package generates internet memes that optionally include a
# superimposed inset plot and other atypical features, combining the visual
# impact of an attention-grabbing meme with graphic results of data analysis.
if (!is.element("memery", installed.packages()[, 1])) {
  install.packages("memery", dependencies = TRUE)
}
require("memery")

## magick - For image processing in R ----
if (!is.element("magick", installed.packages()[, 1])) {
  install.packages("magick", dependencies = TRUE)
}
require("magick")

## yarrr - To create a pirate plot ----
if (!is.element("yarrr", installed.packages()[, 1])) {
  install.packages("yarrr", dependencies = TRUE)
}
require("yarrr")

## radarchart - To create interactive radar charts using ChartJS ----
if (!is.element("radarchart", installed.packages()[, 1])) {
  install.packages("radarchart", dependencies = TRUE)
}
require("radarchart")

## igraph - To create ngram network diagrams ----
if (!is.element("igraph", installed.packages()[, 1])) {
  install.packages("igraph", dependencies = TRUE)
}
require("igraph")

## wordcloud2 - For creating wordcloud by using 'wordcloud2.JS ----
if (!is.element("wordcloud2", installed.packages()[, 1])) {
  install.packages("wordcloud2", dependencies = TRUE)
}
require("wordcloud2")

## readr - Load datasets from CSV files ----
if (!is.element("readr", installed.packages()[, 1])) {
  install.packages("readr", dependencies = TRUE)
}
require("readr")

blue_grey_colours_11 <- c("#27408E", "#304FAF", "#536CB5", "#6981c7", "#8da0db",
                          "#dde5ec", "#c8c9ca", "#B9BCC2", "#A7AAAF", "#888A8E",
                          "#636569")

blue_grey_colours_6 <- c("#27408E", "#304FAF", "#536CB5",
                         "#B9BCC2", "#A7AAAF", "#888A8E")

blue_grey_colours_4 <- c("#27408E", "#536CB5",
                         "#B9BCC2", "#888A8E")

blue_grey_colours_2 <- c("#27408E",
                         "#888A8E")

blue_grey_colours_1 <- c("#6981c7")

# Custom theme for visualizations
blue_grey_theme <- function() {
  theme(
    axis.ticks = element_line(
                              linewidth = 1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    axis.text = element_text(
                             face = "bold", color = "#3f3f41",
                             size = 12, hjust = 0.5),
    axis.title = element_text(face = "bold", color = "#3f3f41",
                              size = 14, hjust = 0.5),
    plot.title = element_text(face = "bold", color = "#3f3f41",
                              size = 16, hjust = 0.5),
    panel.grid = element_line(
                              linewidth = 0.1, linetype = "dashed",
                              lineend = NULL, color = "#dfdede",
                              arrow = NULL, inherit.blank = FALSE),
    panel.background = element_rect(fill = "#f3eeee"),
    legend.title = element_text(face = "plain", color = "#3f3f41",
                                size = 12, hjust = 0),
    legend.position = "right"
  )
}
```

# Course Evaluation Rating per Group and per Gender

This snippet creates a decorated tabular output to display average course evaluation ratings per class group and gender.

```{r Second Code Chunk}
student_performance_dataset <-
  read_csv("data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset.CSV",
           col_types =
             cols(
               class_group = col_factor(levels = c("A", "B", "C")),
               gender = col_factor(levels = c("1", "0")),
               YOB = col_date(format = "%Y"),
               regret_choosing_bi = col_factor(levels = c("1", "0")),
               drop_bi_now = col_factor(levels = c("1", "0")),
               motivator = col_factor(levels = c("1", "0")),
               read_content_before_lecture =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               anticipate_test_questions =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               answer_rhetorical_questions =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               find_terms_I_do_not_know =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               copy_new_terms_in_reading_notebook =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               take_quizzes_and_use_results =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               reorganise_course_outline =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               write_down_important_points =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               space_out_revision =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               studying_in_study_group =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               schedule_appointments =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               goal_oriented = col_factor(levels = c("1", "0")),
               spaced_repetition =
                 col_factor(levels = c("1", "2", "3", "4")),
               testing_and_active_recall =
                 col_factor(levels = c("1", "2", "3", "4")),
               interleaving = col_factor(levels = c("1", "2", "3", "4")),
               categorizing = col_factor(levels = c("1", "2", "3", "4")),
               retrospective_timetable =
                 col_factor(levels = c("1", "2", "3", "4")),
               cornell_notes = col_factor(levels = c("1", "2", "3", "4")),
               sq3r = col_factor(levels = c("1", "2", "3", "4")),
               commute = col_factor(levels = c("1", "2", "3", "4")),
               study_time = col_factor(levels = c("1", "2", "3", "4")),
               repeats_since_Y1 = col_integer(),
               paid_tuition = col_factor(levels = c("0", "1")),
               free_tuition = col_factor(levels = c("0", "1")),
               extra_curricular = col_factor(levels = c("0", "1")),
               sports_extra_curricular = col_factor(levels = c("0", "1")),
               exercise_per_week = col_factor(levels = c("0", "1", "2", "3")),
               meditate = col_factor(levels = c("0", "1", "2", "3")),
               pray = col_factor(levels = c("0", "1", "2", "3")),
               internet = col_factor(levels = c("0", "1")),
               laptop = col_factor(levels = c("0", "1")),
               family_relationships =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               friendships = col_factor(levels = c("1", "2", "3", "4", "5")),
               romantic_relationships =
                 col_factor(levels = c("0", "1", "2", "3", "4")),
               spiritual_wellnes =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               financial_wellness =
                 col_factor(levels = c("1", "2", "3", "4", "5")),
               health = col_factor(levels = c("1", "2", "3", "4", "5")),
               day_out = col_factor(levels = c("0", "1", "2", "3")),
               night_out = col_factor(levels = c("0", "1", "2", "3")),
               alcohol_or_narcotics =
                 col_factor(levels = c("0", "1", "2", "3")),
               mentor = col_factor(levels = c("0", "1")),
               mentor_meetings = col_factor(levels = c("0", "1", "2", "3")),
               `Attendance Waiver Granted: 1 = Yes, 0 = No` =
                 col_factor(levels = c("0", "1")),
               GRADE = col_factor(levels = c("A", "B", "C", "D", "E"))),
           locale = locale())

evaluation_per_group_per_gender <- student_performance_dataset %>% # nolint
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  select(class_group, gender,
         `Student's Gender`, `Average Course Evaluation Rating`) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  group_by(class_group, `Student's Gender`) %>%
  summarise(average_evaluation_rating =
              mean(`Average Course Evaluation Rating`)) %>%
  arrange(desc(average_evaluation_rating), .by_group = TRUE)
evaluation_per_group_per_gender %>%
  rename(`Class Group` = class_group) %>%
  rename(`Average Course Evaluation Rating` = average_evaluation_rating) %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`) %>%
  mutate(`Average Course Evaluation Rating` =
           color_tile("#B9BCC2", "#536CB5")
           (`Average Course Evaluation Rating`)) %>%
  kable("html", escape = FALSE, align = "c",
        caption = "Course Evaluation Rating per Group and per Gender") %>%
  kable_styling(bootstrap_options =
                  c("striped", "condensed", "bordered"),
                full_width = FALSE)
```

This snippet generates a bar chart to visualize average course evaluation ratings per class group and gender.

```{r Third Code Chunk}
evaluation_per_group_per_gender %>%
  ggplot() +
  geom_bar(aes(x = class_group, y = average_evaluation_rating,
               fill = `Student's Gender`),
           stat = "identity", position = "dodge") +
  expand_limits(y = 0) +
  blue_grey_theme() +
  scale_fill_manual(values = blue_grey_colours_2) +
  ggtitle("Course Evaluation Rating per Group and per Gender") +
  labs(x = "Class Group", y = "Average Rating")
```

# Word Count

## Word Count per gender

The following snippet displays the number of significant words in evaluation likes per gender in a tabular format

```{r Fourth Code Chunk}
evaluation_likes_and_wishes <- student_performance_dataset %>%
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  rename(`Class Group` = class_group) %>%
  rename(Likes = `D - 1. Write two things you like about the teaching and learning in this unit so far.`) %>% # nolint
  rename(Wishes = `D - 2. Write at least one recommendation to improve the teaching and learning in this unit (for the remaining weeks in the semester)`) %>% # nolint
  select(`Class Group`,
         `Student's Gender`, `Average Course Evaluation Rating`,
         Likes, Wishes) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  arrange(`Class Group`)

undesirable_words <- c("wow", "lol", "none", "na")

evaluation_likes_filtered <- evaluation_likes_and_wishes %>% # nolint
  unnest_tokens(word, Likes) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Likes (tokenized)` = word) %>%
  select(-Wishes)
word_count_per_gender_likes <- evaluation_likes_filtered %>%
  group_by(`Student's Gender`) %>%
  summarise(num_words = n()) %>%
  arrange(desc(num_words))
  
word_count_per_gender_likes %>%
  mutate(num_words = color_bar("lightblue")(num_words)) %>%
  rename(`Number of Words` = num_words) %>%
  kable("html", escape = FALSE, align = "c",
        caption = "Number of Significant Words in Evaluation Likes 
                   per Gender: Minus contractions, special characters, 
                   stopwords, short words, and censored words.") %>%
  kable_styling(bootstrap_options =
                  c("striped", "condensed", "bordered"),
                full_width = FALSE)
```

The following snippet displays the number of significant words in evaluation wishes per gender in a tabular format

```{r Fifth Code Chunck}
evaluation_likes_and_wishes <- student_performance_dataset %>%
  mutate(`Student's Gender` =
           ifelse(gender == 1, "Male", "Female")) %>%
  rename(`Class Group` = class_group) %>%
  rename(Likes = `D - 1. Write two things you like about the teaching and learning in this unit so far.`) %>% # nolint
  rename(Wishes = `D - 2. Write at least one recommendation to improve the teaching and learning in this unit (for the remaining weeks in the semester)`) %>% # nolint
  select(`Class Group`,
         `Student's Gender`, `Average Course Evaluation Rating`,
         Likes, Wishes) %>%
  filter(!is.na(`Average Course Evaluation Rating`)) %>%
  arrange(`Class Group`)

undesirable_words <- c("wow", "lol", "none", "na")

evaluation_wishes_filtered <- evaluation_likes_and_wishes %>% # nolint
  unnest_tokens(word, Wishes) %>%
  anti_join(stop_words, by = c("word")) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes (tokenized)` = word) %>%
  select(-Likes)

word_count_per_gender_wishes <- evaluation_wishes_filtered %>%
  group_by(`Student's Gender`) %>%
  summarise(num_words = n()) %>%
  arrange(desc(num_words))

 word_count_per_gender_wishes %>%
  mutate(num_words = color_bar("lightblue")(num_words)) %>%
  rename(`Number of Words` = num_words) %>%
  kable("html", escape = FALSE, align = "c",
        caption = "Number of Significant Words in Evaluation Wishes 
                   per Gender: Minus contractions, special characters, 
                   stopwords, short words, and censored words.") %>%
  kable_styling(bootstrap_options =
                  c("striped", "condensed", "bordered"),
                full_width = FALSE)
```

## Top words for Group B students

Displays the most frequently used words in course evaluation likes for students in group B.

```{r Your Sixth Code Chunk}
evaluation_likes_filtered %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Likes (tokenized)`) %>%
  filter(`Class Group` == "B") %>%
  count(`Likes (tokenized)`, sort = TRUE) %>%
  top_n(9) %>%
  mutate(`Likes (tokenized)` = reorder(`Likes (tokenized)`, n)) %>%
  ggplot() +
  geom_col(aes(`Likes (tokenized)`, n), fill = blue_grey_colours_1) +
  blue_grey_theme() +
  xlab("Word in Course Evaluation") +
  ylab("Number of Times Used (Term Frequency)") +
  ggtitle("Most Frequently Used Words in Course Evaluation Likes for Group B
          Students") +
  coord_flip()
```

## Top 10 words for female students

Generates a bar chart showing the most frequently used words in course evaluation wishes by female students

```{r Seventh Code Chunk}
evaluation_wishes_filtered %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Wishes (tokenized)`) %>%
  filter(`Student's Gender` == "Female") %>%
  count(`Wishes (tokenized)`, sort = TRUE) %>%
  top_n(9) %>%
  mutate(`Wishes (tokenized)` = reorder(`Wishes (tokenized)`, n)) %>%
  ggplot() +
  geom_col(aes(`Wishes (tokenized)`, n), fill = blue_grey_colours_1) +
  blue_grey_theme() +
  xlab("Word in Course Evaluation") +
  ylab("Number of Times Used (Term Frequency)") +
  ggtitle("Most Frequently Used Words in Course Evaluation Wishes for Female
          Students") +
  coord_flip()
```

# Word Cloud

## Word Cloud for Evaluation Likes

This code generates a word cloud visualization for evaluation likes, highlighting the most frequently used words.

```{r Eighth Code Chunck}
evaluation_likes_filtered_cloud <- evaluation_likes_filtered %>% # nolint
  count(`Likes (tokenized)`, sort = TRUE)

wordcloud2(evaluation_likes_filtered_cloud, size = .5)
```

## Word Cloud for Evaluation Wishes

This code generates a word cloud visualization for evaluation wishes, highlighting the most frequently used words.

```{r Nineth Code Chunck}
evaluation_wishes_filtered_cloud <- evaluation_wishes_filtered %>% # nolint
  count(`Wishes (tokenized)`, sort = TRUE)

wordcloud2(evaluation_wishes_filtered_cloud, size = .5)
```

# TF-IDF Score

## TF-IDF Score per Group

Calculates and visualizes the TF-IDF (Term Frequency-Inverse Document Frequency) scores for important words in evaluation likes, grouped by class group.

```{r Tenth Code Chunck}
popular_tfidf_words_likes <- evaluation_wishes_filtered %>% # nolint
  unnest_tokens(word, `Wishes (tokenized)`) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes (tokenized)` = word) %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Wishes (tokenized)`) %>%
  count(`Class Group`, `Wishes (tokenized)`, sort = TRUE) %>%
  ungroup() %>%
  bind_tf_idf(`Wishes (tokenized)`, `Class Group`, n)

head(popular_tfidf_words_likes)

top_popular_tfidf_words <- popular_tfidf_words_likes %>%
  arrange(desc(tf_idf)) %>%
  mutate(`Wishes (tokenized)` =
           factor(`Wishes (tokenized)`,
                  levels = rev(unique(`Wishes (tokenized)`)))) %>%
  group_by(`Class Group`) %>%
  slice(seq_len(10)) %>%
  ungroup() %>%
  arrange(`Class Group`, tf_idf) %>%
  mutate(row = row_number())

top_popular_tfidf_words %>%
  ggplot(aes(x = row, tf_idf, fill = `Class Group`)) +
  geom_col(fill = blue_grey_colours_1) +
  blue_grey_theme() +
  labs(x = "Word in Course Evaluation", y = "TF-IDF Score") +
  ggtitle("Important Words using TF-IDF by Chart Level") +
  ggtitle("Most Important Words by TF-IDF Score in Course Evaluation Wishes per 
      Class Group") +
  facet_wrap(~`Class Group`, scales = "free") +
  scale_x_continuous(
                     breaks = top_popular_tfidf_words$row,
                     labels = top_popular_tfidf_words$`Wishes (tokenized)`) +
  coord_flip()
```

## TF-IDF Score per Gender (Wishes)

Calculates and visualizes TF-IDF scores for important words in evaluation wishes, grouped by gender.

```{r Eleventh Code Chunck}
popular_tfidf_words_gender_wishes <- evaluation_wishes_filtered %>% # nolint
  unnest_tokens(word, `Wishes (tokenized)`) %>%
  distinct() %>%
  filter(!word %in% undesirable_words) %>%
  filter(nchar(word) > 3) %>%
  rename(`Wishes (tokenized)` = word) %>%
  select(`Class Group`, `Student's Gender`,
         `Average Course Evaluation Rating`, `Wishes (tokenized)`) %>%
  count(`Student's Gender`, `Wishes (tokenized)`, sort = TRUE) %>%
  ungroup() %>%
  bind_tf_idf(`Wishes (tokenized)`, `Student's Gender`, n)

head(popular_tfidf_words_gender_wishes)

top_popular_tfidf_words <- popular_tfidf_words_gender_wishes %>%
  arrange(desc(tf_idf)) %>%
  mutate(`Wishes (tokenized)` =
           factor(`Wishes (tokenized)`,
                  levels = rev(unique(`Wishes (tokenized)`)))) %>%
  group_by(`Student's Gender`) %>%
  slice(seq_len(10)) %>%
  ungroup() %>%
  arrange(`Student's Gender`, tf_idf) %>%
  mutate(row = row_number())

top_popular_tfidf_words %>%
  ggplot(aes(x = row, tf_idf, fill = `Student's Gender`)) +
  geom_col(fill = blue_grey_colours_1) +
  blue_grey_theme() +
  labs(x = "Word in Course Evaluation", y = "TF-IDF Score") +
  ggtitle("Important Words using TF-IDF by Chart Level") +
  ggtitle("Most Important Words by TF-IDF Score in Course Evaluation Wishes per 
      Class Group") +
  facet_wrap(~`Student's Gender`, scales = "free") +
  scale_x_continuous(
                     breaks = top_popular_tfidf_words$row,
                     labels = top_popular_tfidf_words$`Wishes (tokenized)`) +
  coord_flip()
```
